Quality Definitions of Qualities

### 2019-10-23 StateOfPractice/QDefOfQualities/QDefOfQualities.tex
more quality definitions added

Verifiability involves ``solving the equations right''~\cite[p.~23]{Roache1998};
it benefits from rational documentation that systematically shows, with explicit
traceability, how the governing equations are transformed into code.

\subsection{Validatability}

Validatability means ``solving the right equations''~\cite[p.~23]{Roache1998}.
Validatability is improved by a rational process via clear documentation of the
theory and assumptions, along with an explicit statement of the systematic steps
required for experimental validation.

\subsection{Reliability}

Reliability is a critical quality for scientific software, since the results of
computations are meaningless, if they are not dependable.  Reliability is
closely tied to verifiability, since the key quality to verify is reliability,
while the act of verification itself improves reliability.\\
Reliability models can be used to predict reliability of a software product. For example measuring Mean Time to Fail (MTTF) can be a good measure of reliability \cite{berander2005software}

>>>>

\subsection{Verifiability}
\begin{itemize}
	\item{Definition 1:} A software is verifiable if its properties can be verified (\cite{GhezziEtAl2003}).\\
	\item{Definition 2:} Attributes of software that relate to the effort needed for validating the modified software (\cite{berander2005software}).\\
	\item{Definition 3:}) The degree to which a system or component facilitates the establishment of test criteria and the performance of tests to determine whether those criteria have been met (\cite{IEEEStdGlossarySET1990}).\\
	\item{Definition 4:}  The degree to which a requirement is stated in terms that permit establishment of test criteria and performance (\cite{IEEEStdGlossarySET1990}).\\
	\item{Definition 5:} Ease of performing testing on a software product or system (\cite{IEEEStdGlossarySET1990}).\\
	\item{\textbf{Proposed definition}:} Combo of definitions 4 and 5 ?\\
\end{itemize}
\subsubsection{Discussion}
Verifiability involves ``solving the equations right''~\cite[p.~23]{Roache1998};
it benefits from rational documentation that systematically shows, with explicit
traceability, how the governing equations are transformed into code.
\oo{Verifiability is sometimes referred to as testability, so I culled some testability definitions here}\\
\subsection{Validatability}
\begin{itemize}
\item{Definition 1:} Validatability of a software is the degree of ease in validating(checking) that software meets user needs.\\
\item{Definition 2:} Validatability means ``solving the right equations''~\cite[p.~23]{Roache1998}.
\oo{question about this definition}\\
\item{Definition 3:} The degree of ease of evaluating software products or system to determine whether it satisfies specified business requirements. \url{http://softwaretestingfundamentals.com/verification-vs-validation/}\\
\oo{Here I tweaked the meaning of validation to suit validatability}\\
\oo{Only a few resource on validatability}\\
\item{\textbf{Proposed definition}:} Definition 3
\end{itemize}
\subsubsection{Discussion}
Validatability is improved by a rational process via clear documentation of the
theory and assumptions, along with an explicit statement of the systematic steps
required for experimental validation.

\subsection{Reliability}
\begin{itemize}
	\item{Definition 1:} The probability that the software will operate as expected over a specified time interval (\cite{GhezziEtAl2003}).\\
	\item{Definition 2:} A set of attributes that relate to the capability of software to maintain its level of performance under stated conditions for a stated period of time (\cite{berander2005software}).\\
	\item{Definition 3:} “The capability of the software product to maintain a specified level of performance when used under specified conditions (\cite{international2001iso}).\\
	\item{Definition 4:} Code possesses the characteristic reliability to the extent that it can be expected to perform its intended functions satisfactorily (\cite{boehm2007software})\\
	\item{Definition 5:} A concern encompassing correctness and robustness (\cite{meyer1988object}).\\
	\item{Proposed definition}\\
\end{itemize}

\subsubsection{Discussion}
Reliability is a critical quality for scientific software, since the results of
computations are meaningless, if they are not dependable.  Reliability is
closely tied to verifiability, since the key quality to verify is reliability,
while the act of verification itself improves reliability.\\
Reliability models can be used to predict reliability of a software product. For example measuring Mean Time to Fail (MTTF) can be a good measure of reliability \cite{berander2005software}
